Publishing Datasets about Building Designs \\Based on a Multilayer Building Ontology

### 2015-04-29 article-02-main.tex
Updates from ShareLaTeX

OWL 2 RL has been chosen for \ifcstandard{}, \ifcadvanced{} because in contrast to OWL 2 EL and OWL 2 QL, it supports such needed things as: union data\-types (see \ref{subsec:ifcOWL-select-types}), enumerations of individuals (see \ref{subsec:ifcOWL-enum-types}), anonymous individuals (see \ref{subsec:ifcRDF-naming-individuals}), etc.\cite{w3c:owl2-profiles}.

@@

ifc:IfcComplexProperty a owl:Class ; rdfs:subClassOf ifc:IfcProperty ;
    rdfs:subClassOf [ a owl:Restriction; owl:onProperty ifc:coordinates;
                      owl:allValuesFrom LIST_1_3_IfcLengthMeasure ] ;
    # only for Advanced layer
    rdfs:subClassOf [ a owl:Restriction; owl:onProperty ifc:coordinates;
                      owl:cardinality "1"^^xsd:integer ] .

@@

@@

\subsection{Naming individuals}
\label{ifcRDF:naming-individuals}

>>>>

OWL 2 RL has been chosen for \ifcstandard{}, \ifcadvanced{} because in unlike OWL 2 EL and OWL 2 QL, it supports such needed things as: union data\-types (see \ref{subsec:ifcOWL-select-types}), enumerations of individuals (see \ref{subsec:ifcOWL-enum-types}), anonymous individuals (see \ref{subsec:ifcRDF-naming-individuals}), etc.\cite{w3c:owl2-profiles}.

@@

ifc:IfcComplexProperty a owl:Class ; rdfs:subClassOf ifc:IfcProperty ;
    rdfs:subClassOf [ a owl:Restriction; owl:onProperty ifc:coordinates;
                      owl:allValuesFrom ifc:LIST_1_3_IfcLengthMeasure ] ;
    # only for Advanced layer
    rdfs:subClassOf [ a owl:Restriction; owl:onProperty ifc:coordinates;
                      owl:cardinality "1"^^xsd:integer ] .

@@

Aggregation data\-types may be unordered (\name{SET} and \name{BAG}) or  ordered (\name{LIST} and \name{ARRAY}). \name{BAG} may contain a particular value more than once, unlike \name{SET}. \name{ARRAY} is specified with starting and ending indices while other types are specified with min and max cardinalities.

In order to declare these types, new classes were created in a similar way as Ordered List Ontoloty \cite{olo:ontology}:
\begin{itemize}
\item Class \name{expr:\-Collec\-tion\-Class} has four functional properties: \name{expr:isOrdered}, \name{expr:item\-Type}, \name{expr:\-size}, \name{expr:\-start\-Index}, \name{expr:\-end\-Index} and a nonfunctional property \name{expr:slot} with type \name{expr:Slot}.
\item Class \name{expr:Slot} has two functional properties \name{expr:item} (the actual collection item value), \name{expr:index} and also optional functional properties \name{expr:previous}, \name{expr:next}.
\item Classes \name{expr:SetClass}, \name{expr:ListClass}, \name{expr:ArrayClass} and \name{expr:BagClass} are subclasses of \name{expr:\-Collec\-tion\-Class}.
\end{itemize}

Below is a fragment of definition of type \name{SET [2:?] OF IfcProfileDef}:

\begin{lstlisting}
# all layers:
 ifc:SET_2_UNDEFINED_OF_IfcProfileDef a owl:Class ;
    rdfs:subClassOf ifc:SET_2_UNDEFINED , ifc:SET_OF_IfcProfileDef .

 ifc:SET_2_UNDEFINED, SET_OF_IfcProfileDef a owl:Class ;
    rdfs:subClassOf expr:SetClass .

# only for layer Advanced:
 ifc:SET_2_UNDEFINED rdfs:subClassOf rdfs:subClassOf [ a owl:Restriction ;
    owl:onProperty expr:slot ; owl:minCardinality "2"^^xsd:integer ] .

 ifc:SET_OF_IfcProfileDef rdfs:subClassOf [ a owl:Restriction ;
    owl:onProperty expr:slot ; owl:allValuesFrom ifc:SLOT_OF_IfcProfileDef ].

 ifc:SLOT_OF_IfcProfileDef rdfs:subClassOf [ a owl:Restriction ; owl:onProperty expr:item ; owl:allValuesFrom ifc:IfcProfileDef ] .
\end{lstlisting}

@@

\begin{lstlisting}
:GUID_1916794F-5605-4499-9AB0-F155DE8D3B6C
    a               ifc:IfcPropertySet ; # entity type
    ifc:globalId    [ a ifc:IfcGloballyUniqueId ; # defined/select type
                     rdf:value "0P5dbFLWL4cPgmyLNUZJji"^^xsd:string ] ;
    ifc:hasProperties  _:b11 .

_:b11 a ifc:SET_1_UNLIMITED_OF_IfcProperty ; # entity type
    expr:size "3"^^xsd:integer ;
    expr:itemType ifc:IfcProperty ;
    expr:slot _:b12, _:b13, _:b14 .

_:b12 a ifc:SLOT_OF_IfcProperty ;
    expr:item [ a ifc:IfcPropertySingleValue ; # entity type
                ifc:name "initial_GUID"^^xsd:string ;
                ifc:nominalValue  _:b15 ] .
\end{lstlisting}

\subsection{Metadata}

\TODO {Recommendations about model namespaces, naming individuals, defined types of select types }
